Variability in upwelling patterns across the Benguela upwelling systems

### 2019-10-09 Write_up/Paper1_writeup.Rmd
updated

Sites compared within the OISST datasets showed no difference in the durations of the events at different distances for each of the sites from the coastline. However, there is a difference in the mean intensity of events between sites (*F*=5.74, *SS*=5.2, *p*<0.001). Additionally, there were also significant differences between the mean intensities of events at different distances from the coastline (*F*=260.17, *SS*=78.6, *p*<0.001), and between the durations in events (*F*=51.39, *SS*= 15.53, *p*<0.001) and between sites. Similar comparisons using the CMC dataset showed that there was no significant difference in the duration of events at different distances from the coastline for each of the sites (Three-Way ANOVA: *F*=1.20, *SS*=0.41, *p*>0.05). However, there were significant differences in the mean intensities of events at different distances (*F*=471.63, *SS*=162.0, *p*<0.05), between the durations of events (*F*= 38.36, *SS*=13.2, *p*<0.001), and between sites (*F*=17.64, *SS*=18.2, *p*<0.002). I also found that there was no significant difference between the durations of upwelling across all sites (*F*=0.22, *SS*=0.2, *p*<0.87). When looking at the in situ collected dataset, data collected at the coastline, we find no difference in the durations of events at across sites (*F*=2.05, *SS*=1.84, *p*=0.11) but there was a difference in the mean intensities of those events (*F*=2.05, *SS*=0.61, *p*=0.44).

>>>>

Sites compared within the OISST datasets showed no difference in the durations of the events at different distances for each of the sites from the coastline. However, there is a difference in the mean intensity of events between sites (*F*=5.74, *SS*=5.20, *p*<0.001). Additionally, there were also significant differences between the mean intensities of events at different distances from the coastline (*F*=260.17, *SS*=78.60, *p*<0.001), and between the durations in events (*F*=51.39, *SS*= 15.53, *p*<0.001) and between sites. Similar comparisons using the CMC dataset showed that there was no significant difference in the duration of events at different distances from the coastline for each of the sites (Three-Way ANOVA: *F*=1.20, *SS*=0.41, *p*>0.05). However, there were significant differences in the mean intensities of events at different distances (*F*=471.63, *SS*=162.00, *p*<0.05), between the durations of events (*F*= 38.36, *SS*=13.20, *p*<0.001), and between sites (*F*=17.64, *SS*=18.20, *p*<0.002). I also found that there was no significant difference between the durations of upwelling across all sites (*F*=0.22, *SS*=0.20, *p*<0.87). When looking at the in situ collected dataset, data collected at the coastline, we find no difference in the durations of events at across sites (*F*=2.05, *SS*=1.84, *p*=0.11) but there was a difference in the mean intensities of those events (*F*=2.05, *SS*=0.61, *p*=0.44).
